Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-05-02 hotstorage13/eval.tex
update storage desc

The seek cost of each random IO request in our test machines is about  10 milliseconds.
The average I/O bandwidth of local storage is about 50MB/second 
in the presence of other I/O jobs. Noted that a RAID 0 configuration can deliver
over 300MB/second with 4 drives or more and our setting uses
16.7\% or less of local storage bandwidth. 
The final snapshots are stored in a distributed file system built on the same 
cluster.

>>>>

The seek cost of each random IO request in our test machines is about  10 milliseconds.
The average I/O usage of local storage is controlled about 50MB/second for our backup task
in the presence of other I/O jobs. Noted that a typical 1U server can host
6 to 8  hard drives and deliver over 300MB/second. Our setting uses 16.7\% or less of local storage bandwidth.
The final snapshots are stored in a distributed file system built on the same
cluster.
